---
title: "title"
author: "author"
format:
  html:
    toc: true
    toc-location: right
    theme: minty
    code-fold: true
    code-tools: true
---

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
    warning = FALSE,
    message = FALSE,
    fig.path = "figs/",
    fig.width = 7.252,
    fig.height = 4,
    comment = "#>",
    fig.retina = 3
)
```

# Tip of the week

## How to make an appendix of all your code

To do this, you can first hide all of the code chunks by using the `echo: false` option in the header under the `execute` argument (see more on customizing code chunk execution [here](https://quarto.org/docs/computations/execution-options.html)). Then you can automatically add a copy of all of the code chunks at the end of the document as an appendix! Here's an example:

Let's say I had a code chunk like this:

```{r}
# View the first few rows of the data
head(mtcars)
```

and then I made a chart like this:

```{r}
#| label: scatterplot
#| fig.width: 7
#| fig.height: 4

library(ggplot2)

ggplot(mtcars) + 
    geom_point(aes(x = mpg, y = hp))
```

I could then insert an appendix of all the code chunks in this document like this:

# Appendix

Below is all of the code used to generate this report

```{r}
#| label: get-labels
#| echo: false
#| eval: true

labs <- knitr::all_labels()
```

```{r all-code}
#| eval: false
#| ref.label: labs
```



# Begin notes here


# Reflection
